\documentclass[english]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{hyperref}
\geometry{verbose,tmargin=3cm,bmargin=3cm,lmargin=3cm,rmargin=3cm}

\makeatletter
\usepackage{url}

\makeatother

\usepackage{babel}


\title{Research Plan for Combinatorial Optimisation for Scheduling}
\author{Jasper Vermeulen}
\date{\today}

\newcommand{\namelistlabel}[1]{\mbox{#1}\hfil}
\newenvironment{namelist}[1]{%1
\begin{list}{}
	{
		\let\makelabel\namelistlabel
		\settowidth{\labelwidth}{#1}
		\setlength{\leftmargin}{1.1\labelwidth}
		}
	}{%1
\end{list}}

\begin{document}
\maketitle

\section*{Background of the research}
The problem of scheduling tasks arises in industries all the time. It is not hard to imagine that generating an optimized schedule can be of great profit for production or logistic operations. Optimization can for example be minimizing the overall required time or minimizing the delay before starting a task. Because this type of problem is so prevalent it has already been subject to much research.\\
Formally this specific type of problem is known as the resource-constrained project scheduling problem (RCPSP). On its own the problem definition for RCPSP is to limited to be of use for realistic application. To make sure the researched algorithms solving the scheduling problem would have a wider use case many variations and extensions to the problem definition have been classified over time \cite{RN9}, \cite{RN10}. More recently the variations and extensions have also been surveyed and put into a structured overview \cite{RN6}.\\
For this research the preemptive resource-constrained project scheduling problem with setup times (PRCPSP-ST) variant is under study. Preemption allows an activity to be interrupted during its scheduled time by another activity. Each interruption can be seen as a split of the activity into multiple smaller activities. The setup times are introduced for each interruption in an activity to discourage endless splits resulting in a chaotic schedule. Both a model for allowing preemption \cite{RN21} and including setup times \cite{RN13} have already been established and a proposed algorithm for a combined model was found to result in a reduction of the makespan compared to the optimal schedule without activity preemption \cite{RN1}. Within this algorithm the activities are split into all possible integer time segments and a SAT solver made a selection from these segments \cite{RN3}. The resulting list was used to construct a schedule with a genetic algorithm established in earlier research \cite{RN14}.\\
%What is still missing? This may be much more complex / far into the future than your contribution.

\section*{Research Question}
This research will try to answer the following question:
\begin{quote}
Can the addition of a simple heuristic to a SAT solver algorithm used to solve to PRCPSP-ST models reduce the average makespan of the resulting schedule in an equal amount time?
\end{quote}
Because the RCPSP is known to be strongly NP-hard \cite{RN20} any general algorithm that can be applied to the problem might be outperformed by an algorithm specialized for the specific variation.
To specialize an algorithm this way knowledge or an insight into the problem variation can be translated into a heuristic rule for the algorithm to use. The intention is that this heuristic rule will increase the performance of the algorithm. Because scheduling is so prevalent in industries performance better performing algorithms are desirable ways to increase profits.\\
It has already been shown that allowing for preemption in schedules can lead to a reduction in the resulting makespan even if penalties are given for each activity that is not finished from start to finish \cite{RN1}.
For this research a similar algorithm will be setup that uses a SAT solver algorithm to make a selection of activity segments and constructs a schedule from the selected segments. The expectation for this research is to show that a heuristic version of the SAT solver algorithm will result in a lower makespan when running an equal amount of time.

The answers to the following supporting sub-questions will help towards answering the main research question.
{\begin{itemize}
  \item What is a model for the activities in a RCPSP problem?
  \item How can the RCPSP model be transformed to include activity preemption?
  \item How can setup times be included in the RCPSP model for splits in an activity schedule?
  \item What is the required input of a SAT solver?
  \item How can PRCPSP-ST problems be modelled as an input to a SAT solver for activity segment selection?
  \item What could be a possible heuristic for the SAT solver algorithm?
  \item Where can a heuristic be used by a SAT solver algorithm?
  \item Does the heuristic reduce the resulting activity schedule makespan compared to the default algorithm?
  \item Does the heuristic reduce the time required by the SAT solver algorithm compared to the default algorithm?
\end{itemize}{}}

\section*{Method}
This research will first need a model definition for PRCPSP-ST problems. The model takes a standard RCPSP dataset and includes the possibility for splitting the activities at integer parts for a time penalty trade-off. There are existing activity network for both setup times \cite{RN13} and preemption \cite{RN21} that can be combined. This combined model results in a network that is the same as a standard RCPSP activity network and can therefore be solved by any RCPSP solving algorithm. The extended activity network includes all possible activity segments and needs to be transformed into an input for the SAT solver. For the algorithm to work the input of the SAT solver must force the result to only contain each activity segment once. The SAT solver that is going to be used will be one of the implementations found on \url{https://maxsat-evaluations.github.io/2021/descriptions.html} using the DPLL algorithm \cite{RN18}\cite{RN16}. When the SAT solver returns a selection of segments it can be used to construct a schedule with a minimum makespan. The process going from the combined model to the segment selection has been done in a research before \cite{RN1}.\\
For the construction of the schedule from the selected activity segments the established branch-and-bound algorithm \cite{RN24} can be updated to specific PRCPSP-ST requirements. Previous attempts at altering the branch-and-bound algorithm to include activity preemption has already proven to be successful \cite{RN23}. When the schedule is constructed the objective value must be calculated and for this research it will be the schedule makespan. The algorithm will make multiple iterations within a given time ensuring different results from the SAT solver and when a schedule with a lower makespan is found it is saved. When the time runs out the final makespan is returned.\\

With the first algorithm implementation a baseline benchmark can be generated. Because the RCPSP class of problems is widely studied has a well known and researched dataset \cite{RN25} that can be downloaded at \url{https://www.om-db.wi.tum.de/psplib/data.html}. This will also provide optimal schedule solutions without preemption and setup times to check the quality of the results if necessary.

A last step is including a heuristic in the SAT solver algorithm to make use of problem specific knowledge. If this research is to be successful the resulting set of selected activity segments will result in a lower makespan after the branch-and-bound algorithm is run. A single iteration might take longer but as long as the final makespan after the same given time is lower the heuristic algorithm will be considered more optimal.

\section*{Planning of the research project}
Meetings with the project supervisor and peer group will be held weekly on Wednesdays at 13:00. These meetings are used for feedback on project process and problem resolution.

\subsection{Project timeline}
\begin{tabular}{ l p{0.6\textwidth} l}
  \hline			
  Research phase & Objectives & Deadline \\
  \hline\hline
  1. Background research &
  {\begin{itemize}
    \item Learn about existing research
    \item Gather information on modelling RCPSP problems
    \item Make a model for PRCPSP-ST model variant
    \item Design a complete algorithm from dataset to schedule
    \item Theorize multiple possible heuristics
  \end{itemize}{}} &
  \date{May 6, 2022} \\
  \hline
  2. Implementation &
  {\begin{itemize}
    \item Implement the PRCPSP-ST problem model
    \item Implement a complete algorithm
    \item Add multiple heuristic SAT algorithm alternatives
  \end{itemize}{}} &
  \date{May 20, 2022} \\
  \hline
  3. Performance tests &
  {\begin{itemize}
    \item Generate a baseline benchmark
    \item Test multiple heuristic algorithms vs baseline
    \item Optimize algorithms if necessary
    \item Gather analytical result data
  \end{itemize}{}} &
  \date{June 3, 2022} \\
  \hline
  4. Data analysis and report &
  {\begin{itemize}
    \item Aggregate result data
    \item Perform statistical analysis
    \item Generate (graphical) representations of the data
    \item Report findings on the research question according to data
  \end{itemize}{}} &
  \date{June 17, 2022} \\
  \hline
  5. Presentation &
  {\begin{itemize}
    \item Inform examiner, supervisor and peers on results
  \end{itemize}{}} &
  \date{June 24, 2022} \\
\end{tabular}

\subsection{Deliverables}
\begin{tabular}{ l c }
  \hline			
  Deliverable & Deadline \\
  \hline\hline
  Research proposal: first week plan & \date{April 19, 2022} \\
  Information Literacy & \date{April 20, 2022} \\
  Research proposal: a document describing  what will be done and when & \date{April 24, 2022} \\
  Research proposal presentation & \date{April 24, 2022} \\
  Academic Communication Skills: First 300 words & \date{May 7, 2022} \\
  Academic Communication Skills: Midterm poster (for feedback) & \date{May 12, 2022} \\
  Midterm presentation (+ poster) & \date{May 16, 2022} \\
  Academic Communication Skills: Improve first 300 words, and add section (300 words) & \date{May 19, 2022} \\
  Scientific paper: v1 for peer feedback on writing and content feedback by supervisor & \date{May 30, 2022} \\
  Peer review on v1 paper from another student & \date{June 2, 2022} \\
  Scientific paper: v2 for feedback on both content and writing by supervisor & \date{June 8, 2022} \\
  Poster summarizing research & \date{June 17, 2022} \\
  Scientific paper: final version & \date{June 19, 2022} \\
  Software programmed to obtain results & \date{June 19, 2022} \\
\end{tabular}

\bibliographystyle{plain}
\bibliography{ProposalBib}
\end{document}
