\section{Introduction} \label{section:introduction}
The problem of scheduling tasks arises in industries all the time. It is not hard to imagine that generating an optimised schedule can be of great profit for production or logistic operations. For example, optimisation can minimise the overall required time or minimise the delay before starting a task. Because this type of problem is so prevalent it has already been subject to much research.

Formally this specific type of problem is known as the resource-constrained project scheduling problem (RCPSP) \cite{RN69, RN66, RN70}. Problems of this type are considering the allocation of tasks to resources within a project. Tasks are anything that needs to be done during a project. Examples could be work performed by people or a simulation run by a computer. Resources are made available for a project like experts assigned to the project or time reserved on computers to run simulations. Tasks are given a duration required to finish and a required amount of a resource during processing. Resources are limited in availability during the project, eg. only one expert is available at a single moment in time so multiple tasks requiring an expert must be processed consecutive. An important addition to this setup is the order in which pairs of tasks must be processed. Some tasks require another task to be finished before it can be started. This requirement is referred to as a precedence constraint.

It can be required by an application of an algorithm to include additional constraints on schedules. To provide for these additional constraints variations and extensions to the problem definition have been classified over time \cite{RN9}, \cite{RN10}. More recently, the variations and extensions have also been surveyed and put into a structured overview \cite{RN6}.

%mention the importance of your variant in specific. For example, why does adding preemption increase “realism”? Where can it be used? 

For this research, the preemptive resource-constrained project scheduling problem with setup times (PRCPSP-ST) variant is under study. Preemption allows a task to be interrupted during its scheduled time by another task. Each interruption can be seen as splitting the task into multiple smaller activities. The setup times are introduced for each interruption in a task to discourage endless splits resulting in a chaotic schedule. A model for allowing preemption \cite{RN21} and a model including setup times \cite{RN13} have already been established. Both models have been combined and a proposed algorithm for it was found to result in a reduction of the makespan compared to the optimal schedule without task preemption \cite{RN1}. Within this algorithm, the activities are split into all possible integer time segments and a satisfiability (SAT) solver selects a feasible subset from these segments \cite{RN3}. The resulting list was used to construct a schedule with a genetic algorithm established in earlier research \cite{RN14}.

In the research done on solving RCPSP variants, the recent focus has been on heuristic and meta-heuristic algorithms. These algorithms are usually variants of branch-and-bound algorithm \cite{RN21} or a form of genetic algorithms \cite{RN28} that were established for the standard RCPSP.

SAT solvers are a general tool that can be used on any algorithmic problem if it is encoded as the required input for the solver. A SAT solver is a program that tries to solve Boolean satisfiability problems. Boolean satisfiability problems are a set of true or false variables that are set up in a formula with ‘AND’ and ‘OR’ operators (sets of variables and operators are often referred to as clauses). The SAT solver tries to assign values to all variables in such a way that the outcome of the overall formula becomes true (also referred to as being satisfied). If a Boolean formula encoding can be found for a problem, a SAT solver can be used to try and solve it. In addition to finding a solution to the problem, it can include information about the solution it provides like the assignment for the variables it found or a minimal set of unsatisfiable clauses.

SAT solvers have been used as a part of the algorithm but using them as a complete solution to try and solve PRCPSP-ST instances has not been researched before. Because RCPSP is known to be strongly NP-hard \cite{RN20}, a SAT solver might not be efficient enough to outperform the heuristic and meta-heuristic methods. But what a SAT solver does provide is a way to prove if a found solution is optimal and can therefore not be improved further. When looking for a reduction in makespan getting confirmation on optimality might be worth some possible trade-offs a SAT solver introduces.

Because there is room to try and find out if a SAT solver can match or even outperform the heuristic and meta-heuristic algorithms the main research question considered in this paper is \textit{Can a satisfiability encoding of PRCPSP-ST models solved on a SAT solver be used to reduce the average makespan of the resulting schedule compared to a heuristic algorithm when run for an equal amount time?}.

This paper first proposes a heuristic algorithm that can solve the extended RCPSP instances with preemption and setup times. This algorithm is used to produce a baseline result for the instances in three datasets. And then, a satisfiability encoding for the instances is run on a SAT solver for an equal amount of time. The results are compared, and it shows that the SAT solver approach does struggle with coming up with an initial solution in many cases when the time limit is strict. It does make up for it by providing better solutions in almost all cases and providing proof of optimality in over half of its results. For applications of a satisfiability approach, the trade-off between always having a solution compared to knowing when a solution is optimal will have to be considered.

The following sections of this paper can be summarized as follows. Section \ref{section:problem_formulation} gives the formal definition of the RCPSP and PRCPSP-ST problems followed by an overview of research done in the field of solving the PRCPSP-ST problem. Section \ref{section:your_contribution} describes the heuristic algorithm used to generate baseline results and the Boolean logic encoding for the PRCPSP-ST problems and the SAT solver that will be used during testing. Next, section \ref{section:experimental_setup} outlines the experiments that are going to be run to test the performance of both algorithms and it presents the result data from the experiments. A short reflection on the ethical implications of competition for the next state-of-the-art solution is given in section \ref{section:responsible_research}. The results are discussed in section \ref{section:discussion}. Section \ref{section:conclusion} concludes the research and motivates where future research could be focused on.